### 2019-09-03 paper/HOLMultivariate.tex
Fixed TRANS_IMP_NO_NIL (CCSTheory)
Updated generated TeX code (stable now)

\newcommand{\HOLMultivariateTime}{10:42}

@@

       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}

@@

       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
       \HOLKeyword{else} \HOLConst{\ensuremath{\mu}} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})

@@

       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{R} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolution}
       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{STRONG_EQUIV} \HOLSymConst{\HOLTokenConj{}}
           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{STRONG_EQUIV} \HOLSymConst{\HOLTokenImp{}}
\newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolution}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolution}}

@@

@@

       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps} \HOLBoundVar{Qs}.
           \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenConj{}}
           \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}

@@

                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

                    (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenImp{} \HOLBoundVar{y}))

@@

               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenImp{} \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{CCS_solution} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLConst{OBS_contracts} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{\ensuremath{\mu}} \HOLBoundVar{Y} \HOLBoundVar{E})

@@

\HOLThmTag{Multivariate}{strong_unique_solution}\HOLMultivariateTheoremsstrongXXuniqueXXsolution

@@

>>>>

\newcommand{\HOLMultivariateTime}{14:31}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps}.
       \HOLConst{CCS_solution} \HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}

@@

       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\HOLTokenBackslash{}\HOLTokenBackslash{}} \HOLBoundVar{X}) \HOLBoundVar{E})
       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})

@@

       \HOLConst{CCS_equation} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{CCS_solution} \HOLBoundVar{R} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{context} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}

@@

@@

\begin{SaveVerbatim}{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm}
       \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{STRONG_EQUIV} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
       \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{STRONG_EQUIV} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}
\newcommand{\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm}{\UseVerbatim{HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm}}

@@

       \HOLBoundVar{Ps} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenConj{}}
       \HOLBoundVar{Qs} \HOLConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Qs} \HOLSymConst{\HOLTokenImp{}}

@@

                \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

                    (\HOLConst{WEAK_EQUIV} \HOLConst{O} (\HOLTokenLambda{}\HOLBoundVar{x} \HOLBoundVar{y}. \HOLBoundVar{x} \HOLTokenWeakTransBegin\HOLConst{label} \HOLBoundVar{l}\HOLTokenWeakTransEnd \HOLBoundVar{y}))

@@

               \HOLConst{CCS_SUBST} (\HOLBoundVar{Xs} \HOLSymConst{\HOLTokenMapto{}} \HOLBoundVar{Ps}) \HOLBoundVar{C} \HOLTokenWeakTransBegin\HOLConst{\ensuremath{\tau}}\HOLTokenWeakTransEnd \HOLBoundVar{R} \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLBoundVar{Xs} \HOLBoundVar{Es} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{context} \HOLBoundVar{Xs} \HOLFreeVar{C} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenImp{}}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} (\HOLConst{rec} \HOLBoundVar{Y} \HOLBoundVar{E})

@@

@@

\HOLThmTag{Multivariate}{strong_unique_solution_thm}\HOLMultivariateTheoremsstrongXXuniqueXXsolutionXXthm
